Clean 2015 Raw Data

### 2018-04-25 data-raw/README.Rmd
Change field names in N_management tibble

>>>>

# Nitrogen management data

Create a `tibble` object of the N treatments for use in the paper as a table.

N_management <- tibble::tibble(
  `Nitrogen treatment` = character(),
  Year = integer(),
  `Total N (kg/ha)` = integer(),
  `Basal` = integer(),
  `Tillering` = integer(),
  `Panicle Initiation` = integer()
  )

  N_management <-
  tibble::add_row(N_management,
  `Nitrogen treatment` = c("N0",
  "N100",
  "N120",
  "N60",
  "N180"))

  N_management$Year <- c(2015,
  2015,
  2015,
  2016,
  2016)

  N_management$`Total N (kg/ha)` <- c(0,
  100,
  120,
  60,
  180)

  N_management$Basal <- c(0,
  60,
  60,
  30,
  60)

  N_management$Tillering <- c(0,
  20,
  30,
  30,
  60)

  N_management$`Panicle Initiation` <- c(0,
  20,
  30,
  0,
  60)

  N_management

devtools::use_data(N_management,
                   compress = "bzip2",
                   overwrite = TRUE)
```

# Colophon

```{r}
sessioninfo::session_info()
```
